Two photon coupling to atomic relative motional continuum

### 2020-12-01 two-photon.tex
WIP: two photon scattering

As shown in Fig.~\todo{}, since we only have the two Raman frequencies in the experiment,
the energy of the final state is never higher than that of the initial atomic state
and well below the corresponding trap depth.
Therefore, in order to couple to the continuum,
the final state must belong to a different atomic spin state with lower energy.
For our initial spin state of $\Na(2,2),\Cs(3,3)$,
the only candidate for such state is therefore $\Na(1,1),\Cs(3,3)$,
which is lower in energy by $\approx\!1.77~\mathrm{GHz}$.

>>>>

\begin{figure}[ht!]
  \includegraphics[width=0.6\textwidth]{imgs/pa_two_photon_down_raman.pdf}
  \caption{
    Effect of two-photon coupling to atomic contimuum on molecular state.
    (a) Raman transition from the atomic ground state $|g\rangle$
    to the molecular bound state $|m\rangle$ using two Raman beams with frequencies
    $\omega_1$ and $\omega_2$.
    (b-e) Two photon transitions starting from the molecular state $|m\rangle$
    with different frequency combinations without additional atomic spin states.
    (b) This is the reverse Raman transition and reaches the initial atomic state.
    (c,d) The frequency pairs couples back to $|m\rangle$.
    (e) This couples to an energy below $|m\rangle$.
    Note that none of the two-photon transitions from $|m\rangle$ in (b-e) ends up in
    the atomic motional continuum (gray) for the spin state $|g\rangle$.
    However, it is coupled to the motional continuum
    for the spin state with lower energy $|g'\rangle$
    and may be affected by the corresponding dissociative scattering.
    \label{f-raman-continuum}}
\end{figure}

As shown in Fig.~\ref{f-raman-continuum},
since we only have the two Raman frequencies in the experiment,
the energy of the final state is never higher than that of the initial atomic state
and well below the corresponding trap depth.
Therefore, in order to couple to the continuum,
the final state must belong to a different atomic spin state with lower energy.
For our initial spin state of $\Na(2,2),\Cs(3,3)$,
the only candidate for such state is therefore $\Na(1,1),\Cs(3,3)$,
which is lower in energy by $\approx\!1.77~\mathrm{GHz}$.
